A perfect storm and the natural endowments of trade-enabling infrastructure

### 2023-07-22 Slides/10min/10min.Rmd
Update readme with 10 min slides
Fixed non-loading figure pop_MA
updated 10 min.

**15/45**

@@

![Descriptive](Figures/Ship_trafic.png)
---
name: str-results
# The channel caused trade
.pull-left[
- **Data**: Panel of Danish ports 1750-1855 
- **Outcome**: Cargo ship traffic with origin or destination in a specified port
- PPML estimator following Silva & Tenreyro (2006) 
- In the order of 400% growth in trade in the region
- Local descriptive trade stats show the same story:
  + From 6 to 62 ships in Thisted harbour (1834-1876)
  + 997% increase in oats export, Thisted (1801-1853) 
]

@@

>>>>

@@

![Descriptive](Figures/Ship_trafic.png)

@@

---
name: str-results
# The channel caused trade
.pull-left[
- **Data**: Panel of Danish ports 1750-1855 
- **Outcome**: Cargo ship traffic with origin or destination in a specified port
- PPML estimator following Silva & Tenreyro (2006) 
- In the order of 400% growth in trade in the region
- Local descriptive trade stats show the same story:
  + From 6 to 62 ships in Thisted harbour (1834-1876)
  + 997% increase in oats export, Thisted (1801-1853) 
]
